\documentclass{article}
\usepackage{graphicx}
\usepackage{tabularx,booktabs}
\usepackage[english]{babel} 
\usepackage[margin=1in]{geometry}

\setcounter{secnumdepth}{0}
\renewcommand{\baselinestretch}{1.15}

\begin{document}

\title{LEE Analyser Tree}
\author{Wouter Van De Pontseele}

\maketitle

\tableofcontents
\section*{Introduction}
Every field will start with \textbf{name}, \textbf{type}, \textbf{Reco or truth info}.
\clearpage

\section{Definitions of fields}
\begin{enumerate}


\item \textbf{category} \hfill UInt\_t, Truth \\ \\
Possible values: \\ \\
\begin{tabularx}{\linewidth}{lX}
k\_cosmic = 1 & There was no neutrino generated in the event. Or, the selected PNC has only reconstructed tracks/showers that are matched to cosmic origin.\\
k\_nu\_e = 2  & Generated neutrino inside TPC and $\nu_e$. And, the selected PNC has only  reconstructed tracks/showers that are matched to neutrino origin.\\
k\_nu\_mu = 3 & Generated neutrino inside TPC and $\nu_\mu$. And, the selected PNC has only  reconstructed tracks/showers that are matched to neutrino origin.\\
k\_nc = 4 & Generated neutrino interaction is NC (in/out TPC). And, the selected PNC has  only reconstructed tracks/showers that are matched to neutrino origin.\\
k\_dirt = 5 & Generated neutrino interaction was not NC and outside the TPC active volume. \\
k\_data = 6 & Data, no truth info available. \\
k\_mixed = 7 & The selected PNC has reconstructed tracks/showers that are matched to neutrino and cosmic origin. \\
k\_other = 0 & None of the reconstructed tracks/showers of the selected PNC could be matched to cosmic/neutrino origin. (Can only be used if the category was not k\_dirt already.)
\end{tabularx}
\vspace{5mm}


\item \textbf{reconstructed\_energy } \hfill $vector<double>$, Reco \\ \\ 
Sum of the reconstructed energy of the tracks/showers (see definitions) associated to the selected PNC. Three values for the three planes, given in GeV.
\vspace{5mm}

\item \textbf{n\_tracks}  \hfill UInt\_t, Reco \\ \\ 
blabla
\vspace{5mm}


\end{enumerate}
\clearpage
\setcounter{secnumdepth}{1}
\appendix
\section{List of types}

\vspace{3mm}
\begin{tabular}{ll}
UInt\_t & A 32 bit unsigned integer. \\

\end{tabular}
\vspace{3mm}

\section{List of abbreviations}
\vspace{3mm}
\begin{tabular}{ll}
PNC & Pandora neutrino candidate particle flow particle \\
TPC & Time projection chamber \\
NC  & neutral current 

\end{tabular}
\vspace{3mm}


\end{document}
